---
title: "Made in America Yarns"
subtitle: "September, 2020"
output: 
  html_document:
    fig_width: 6
    fig_height: 4
params: 
  yearmo: "202009"
---


```{r setup, include=FALSE}

#echo=TRUE means that the code shows
knitr::opts_chunk$set(echo = FALSE, fig.align = "center")

library(tidyverse)

yearmo <- params$yearmo

#IMPORT DATA
orders <- read.csv(paste("C:/Users/Owner/repos/miay/data/", yearmo, "/processed/orders_", yearmo, ".csv",sep=""), stringsAsFactors = FALSE)
registrations <- read.csv(paste("C:/Users/Owner/repos/miay/data/", yearmo, "/processed/registrations_", yearmo, ".csv",sep=""), stringsAsFactors = FALSE)
traffic <- read.csv(paste("C:/Users/Owner/repos/miay/data/", yearmo, "/processed/traffic_", yearmo, ".csv",sep=""), stringsAsFactors = FALSE)
coupon <- read.csv(paste("C:/Users/Owner/repos/miay/data/", yearmo, "/processed/coupon_", yearmo, ".csv",sep=""), stringsAsFactors = FALSE)
campaign <- read.csv(paste("C:/Users/Owner/repos/miay/data/", yearmo, "/processed/campaign_", yearmo, ".csv",sep=""), stringsAsFactors = FALSE)

style <- theme(plot.title = element_text(face = "bold", size = 15),
               axis.title = element_text(size = 13, face="italic"),
               axis.text = element_text(size = 13),
               legend.text = element_text(size = 13),
               legend.title = element_text(face = "bold", size = 13),
               legend.position = "bottom",
               panel.background = element_rect(fill = NA),
               panel.grid.major = element_line(colour = "grey88"),
               axis.ticks = element_line(color=NA),
               axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)),
               axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)),
               strip.background = element_rect(colour = "grey40", fill = NA),
               strip.text = element_text(size=10))

geom_col_base <- geom_col(fill="darkgoldenrod4", alpha=0.6, width=0.5)

```


<script type="text/javascript">
  // When the document is fully rendered...
  $(document).ready(function() {
    // ...select all header elements...
    $('h1, h2, h3, h4, h5').each(function() {
      // ...and add an id to them corresponding to their 'titles'
      $(this).attr('id', $(this).html());
    });
  });
</script>


```{css}

h1, h2, h3, p {text-align: center;}
p {font-size: 16px}

```
<br></br>
<br></br>

# Contents

<br></br>
<a href="#Conversions">Conversions</a>
<br></br>
<a href="#Sales">Sales</a>
<br></br>
<a href="#Traffic">Traffic</a>
<br></br>
<a href="#Coupons">Coupons</a>
<br></br>
<a href="#Campaigns">Campaigns</a>

<br></br>
<br></br>

# Conversions

<a href="#Made in America Yarns">return to top</a>
<br></br>

A conversion happens when a user's role in relation to Made in America Yarns changes. When a user subscribes to the newsletter, they become a subscriber. When a user creates an account, they become a registered user. When a user places an order, they become a customer. Conversions for newsletter signups, registrations, and new customers are shown below.


```{r message=FALSE, warning=FALSE, fig.height=2}

# VALUE BOX (conversions)
#------------------------------>

# assign variables

vb_newsletter_signup <- as.character(sum(traffic$newsletter_sign_up, registrations$customer_registrations))
vb_register <- as.character(sum(registrations$customer_registrations))
vb_new_cust <- as.character(sum(orders$new_customers))

# create df of parameters

df <- data.frame(
  x = seq(2, 22, 10), # position of box
  y = rep(1,3), # position of box
  h = rep(7,3), # size of box
  w = rep(11,3), # size of box
  value = c(vb_newsletter_signup,
            vb_register,
            vb_new_cust),
  info_top = c("newsletter",
           "",
           "new"),
  info_bottom = c("signups",
           "registrations",
           "customers")
)

# plot df created above

vb_plot <- function(df){
  df %>% 
  ggplot(aes(x, y, height = 7, width = 9)) +
  geom_tile(color="orange4", size=2, fill="cornsilk") +
  geom_text(color = "darkblue", fontface = "bold", size = 10, #size of info
            aes(label = value,y=y+1)) +
  geom_text(color = "darkblue", fontface = "bold", size = 5,
            aes(label = info_top, y=y-0.9)) + #size of value
  geom_text(color = "darkblue", fontface = "bold", size = 5,
            aes(label = info_bottom, y=y-2)) + #size of value
  theme_void() +
  theme(legend.position="none") +
  coord_fixed() 
}

vb_plot(df)
```

<br></br>
<br></br>

# Sales

<a href="#Made in America Yarns">return to top</a>
<br></br>

Turnover is equal to product price multiplied by quantity. Net profit is equal to turnover minus losses due to shipping, refunds, coupons, and paypal fees. Expense and order insights are shown below.

```{r message=FALSE, warning=FALSE}

# VALUE BOX (sales)
#------------------------------>

# assign variables

vb_turnover <- round(sum(orders$turnover),0)
vb_net <- round(sum(orders$net_profit),0)
vb_orders <- sum(orders$orders_placed)
vb_aov <- round(vb_turnover/vb_orders, 0)
vb_ppo <- floor(mean(replace_na(orders$products_purchased/orders$orders_placed, 0)))

# create df of parameters

df <- data.frame(
  x = c(7,17,2,12,22), # position of box
  y = c(9,9,1,1,1), # position of box
  h = rep(5,5), # size of box
  w = rep(9,5), # size of box
  value = c(paste("$", formatC(vb_turnover, format = 'd', big.mark = ','), sep=""),
            paste("$", formatC(vb_net, format = 'd', big.mark = ','), sep=""),
            vb_orders,
            paste("$", formatC(vb_aov, format = 'd', big.mark = ','), sep=""),
            vb_ppo),
  info_top = c("",
           "",
           "",
           "average",
           "products"),
  info_bottom = c("turnover",
           "net profit",
           "orders placed",
           "order value",
           "per order")
)

vb_plot(df)

```

<br></br>
<br></br>

```{r message=FALSE, warning=FALSE}

# PLOT (profits and losses)
#------------------------------>

vrs <- c("turnover", "net_profit", "discounts", "refunds", "fee_paypal", "shipping_charged",
         "shipping_cost")

df <- orders %>% 
  #calculate totals for month
  summarise(across(all_of(vrs), sum)) %>% 
  #pivot variables to values
  pivot_longer(cols=everything()) %>%
  #reorder variables
  mutate(name = factor(str_replace_all(name,"_", " "), levels = c("turnover", 
                                        "net profit", 
                                        "shipping charged", 
                                        "shipping cost", 
                                        "discounts", 
                                        "refunds", 
                                        "fee paypal")),
         category = case_when(name %in% c("turnover", 
                                          "shipping charged") ~ "profit",
                              name %in% c("shipping cost", 
                                          "discounts", 
                                          "refunds", 
                                          "fee paypal") ~ "loss",
                              name == "net profit" ~ "net profit"))

cols <- c("profit"="darkolivegreen", 
          "net profit"="darkgoldenrod4",
          "loss"="indianred4")

df %>%
  ggplot(aes(x = name, 
             y = value,
             fill = factor(category))) +
  labs(title="Profits and Losses",
       x="",
       y="") +  
  geom_col(alpha = 0.8, width=0.8) +
  geom_text(label = paste("$", formatC(df$value, format = 'd', big.mark = ','), sep=""),
            y = df$value + 300,
            size = 3) +
  scale_colour_manual(
    values = cols,
    aesthetics = c("color", "fill"),
    name = "") +
  expand_limits(y=c(0,vb_turnover+500)) +
  scale_y_continuous(labels = scales::dollar) +
  style + theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))


```

<br></br>
<br></br>

```{r message=FALSE, warning=FALSE}
# PLOT (orders placed by new vs returning customers)
#------------------------------>

df <- orders %>% 
  mutate("returning" = abs(orders_placed - new_customers),
         "new" = new_customers,
         "order_day" = lubridate::day(order_date)) %>%
  select(order_day, 
         returning,
         new) %>%
  pivot_longer(!order_day,
               names_to = "customer_type",
               values_to = "orders_placed")

cols <- c("new" = "darkolivegreen4",
          "returning" = "darkgreen")

df %>% 
  ggplot(aes(x = order_day, y = orders_placed, fill = factor(customer_type))) +
  labs(title="Orders Placed by New and Returning Customers",
       x="day of month",
       y="number of orders placed") +
  geom_col(position = "stack", alpha=0.8, width=0.8) +
  scale_colour_manual(
  values = cols,
  aesthetics = c("color", "fill"),
  name="customer type") +
  style 

```
<br></br>
<br></br>

# Traffic

<a href="#Made in America Yarns">return to top</a>
<br></br>

Where are users coming from and how are they interacting with madeinamericayarns.com? This section shows how users behave throughout checkout and where users and newsletter subscribers come from. 

````{r message=FALSE, warning=FALSE}

# VALUE BOX (traffic)
#------------------------------>

# assign variables

vb_users <- sum(traffic$users)
vb_pct_new_users <- round(sum(traffic$new_users)/sum(traffic$users)*100, 0)
vb_pct_view_cart <- round(sum(traffic$view_cart)/sum(traffic$user)*100, 0)
vb_pct_reach_checkout <- round(sum(traffic$reach_checkout)/sum(traffic$user)*100, 0)

# create df of parameters

df <- data.frame(
  x = c(12,2,12,22), # position of box
  y = c(9,1,1,1), # position of box
  h = rep(5,4), # size of box
  w = rep(9,4), # size of box
  value = c(formatC(vb_users, format = 'd', big.mark = ','),
            paste(vb_pct_new_users, "%",sep=""),
            paste(vb_pct_view_cart, "%",sep=""),
            paste(vb_pct_reach_checkout, "%",sep="")),
  info_top = c("",
           "",
           "viewed",
           "reached"),
  info_bottom = c("unique users",
           "new users",
           "their cart",
           "checkout")
)

vb_plot(df)

```

**How do users behave throughout checkout?**
<br></br>
Users who view their cart but do not reach checkout might not be interested enough in the product. Users who reach checkout but do not place an order might be deterred by price. Understanding user behavior throughout checkout can help optimize the checkout process.

<br></br>
<br></br>

```{r message=FALSE, warning=FALSE}

# PLOT (order funnel)
#------------------------------>

df <- data.frame("orders_placed" = sum(orders$orders_placed), 
                 "checkout_page_views" = sum(traffic$reach_checkout), 
                 "cart_views" = sum(traffic$view_cart))

df <- df %>% 
  pivot_longer(cols=everything()) %>%
  mutate(name = case_when(name == "cart_views" ~"viewed cart",
                          name == "checkout_page_views" ~"reached checkout",
                          name == "orders_placed" ~"placed an order")) %>%
  mutate(name = factor(name, levels = c("viewed cart", "reached checkout", "placed an order")))
           

cols <- c("placed an order"="darkgreen",
          "reached checkout"="darkolivegreen4", 
          "viewed cart"="darkolivegreen2")

df %>% 
  ggplot(aes(x = name, y=value, fill=name)) +
  labs(title="Order Funnel",
       x="event",
       y="number of occurrences") +
  geom_col(alpha = 0.8, width = 0.5) +
  geom_text(label = df$value,
            y = df$value + 4) +
  expand_limits(y=c(0,max(df$value+5))) +
  scale_color_manual(values = cols,
                     aesthetics = c("color", "fill"),
                     guide = FALSE) +
  style

```

**Where do users come from?** 
<br></br>
The **source** is the exact url where a user was before arriving at madeinamericayarns.com. 

<br></br>
<br></br>

```{r message=FALSE, warning=FALSE}

# PLOT (newsletter signup sources)

df <- traffic %>% 
  #group by source
  group_by(source) %>%
  #sum newsletter_signups by source
  summarise(newsletter_sign_up = sum(newsletter_sign_up)) %>%
  filter(newsletter_sign_up != 0)

# order by newsletter signups
df$source <- factor(df$source, levels = df$source[order(df$newsletter_sign_up)])

df %>%
  ggplot(aes(x = source,
             y = newsletter_sign_up,
             fill = medium)) +
  geom_col_base +
  labs(title="Newsletter Subscribers",
       x="source",
       y="number of newsletter signups") +
  coord_flip() +
  style 

```

<br></br>
<br></br>

```{r message=FALSE, warning=FALSE}

# PLOT (all users)
#------------------------------>

df <- traffic %>% 
  #group by source/medium
  group_by(source, medium) %>%
  #format source/medium for label
  summarise("sessions" = sum(users)) %>%
  filter(sessions >= 10,
         source != "google") %>%
  select(source,
         medium, 
         sessions) 

# order by sessions
df$source <- factor(df$source, levels = df$source[order(df$sessions)])

df %>%
  ggplot(aes(x = source, y = sessions)) + 
  geom_col_base +
  labs(title="All Users",
       x="source",
       y="number of website visits") +
  coord_flip() +
  style 

```
<br></br>
<br></br>

# Coupons

<a href="#Made in America Yarns">return to top</a>
<br></br>

Knowing the discounts and number of applications for each coupon can help identify effective promotions. Consider two coupons that were applied the same number of times but result in different amounts in discounts. One could infer that customers were equally interested in both coupons, but the coupon that resulted in less discounts makes more sense from a business perspective.

<br></br>
<br></br>

```{r message=FALSE, warning=FALSE, fig.height=2}


# VALUE BOX (coupons)
#------------------------------>

# assign variables

vb_coupon_orders <- sum(coupon$total_orders)
vb_coupon_discounts <- sum(coupon$total_discounts)

# create df of parameters

df <- data.frame(
  x = c(2,12), # position of box
  y = c(1,1), # position of box
  h = rep(5,2), # size of box
  w = rep(9,2), # size of box
  value = c(vb_coupon_orders,
            paste("$",formatC(vb_coupon_discounts, format = 'd', big.mark = ','), sep="")),
  info_top = c("total coupon",
           ""),
  info_bottom = c("applications",
           "total discounts")
)

vb_plot(df)

```

<br></br>
<br></br>

```{r message=FALSE, warning=FALSE}

# PLOT (discounts)
#------------------------------>

df <- coupon

#amount discounted
df %>% 
  ggplot(aes(x = coupon_code, y = total_discounts)) +
  geom_col(fill="indianred4", alpha=0.6, width=0.5) +
  labs(title="Discounts",
       x="coupon code",
       y="amount discounted") +
  scale_y_continuous(labels = scales::dollar) +
  style 

```

<br></br>
<br></br>

```{r message=FALSE, warning=FALSE}
#PLOT (coupon applications)
#------------------------------>

df %>% 
  ggplot(aes(x = coupon_code, y = total_orders)) +
  geom_col_base +
  labs(title="Coupon Applications",
       x="coupon code",
       y="number of applications") +
  style 



```
<br></br>
<br></br>

# Campaigns

<a href="#Made in America Yarns">return to top</a>
<br></br>

Each newsletter and facebook post contains a unique link which makes it possible to measure the performance of the campaign. The charts below show the number of times each campaign link was clicked and how the resulting users behaved throughout checkout.

<br></br>
<br></br>

```{r, message=FALSE, warning=FALSE}

# PLOT (campaign clicks)
#------------------------------>

df <- campaign %>%
  pivot_longer(!c(source, campaign), names_to = "metric", values_to = "value") %>%
  filter(metric == "click")

cols <- c("facebook" = "steelblue",
          "newsletter" = "gold1")

df %>% ggplot(aes(x = campaign, y = value, fill = factor(source))) +
  labs(title="Campaign Link Clicks",
       x="campaign",
       y="number of clicks") +
  geom_col(position = "stack", alpha = 0.8, width = 0.5) +
  scale_color_manual(values = cols,
                     aesthetics = c("color", "fill"),
                     name="source",
                     guide = FALSE) +
  style 
```

<br></br>
<br></br>

```{r, message=FALSE, warning=FALSE}
# PLOT (campaign order funnel)
#------------------------------>

df <- campaign %>%
  pivot_longer(!c(source, campaign), names_to = "metric", values_to = "value") %>%
  filter(metric != "click") %>%
  mutate(metric = case_when(metric == "view_cart" ~"viewed cart",
                          metric == "reach_checkout" ~"reached checkout")) 

cols <- c("facebook" = "steelblue",
          "newsletter" = "gold1")

df %>% ggplot(aes(x = metric, y = value, fill = source)) +
  labs(title="Campaign Order Funnel",
       x="event",
       y="number of occurences") +
  facet_wrap(~campaign) +
  geom_col(position = "stack", alpha = 0.8, width=0.5) +
  scale_color_manual(values = cols,
                     aesthetics = c("color", "fill")) +
  style + theme(panel.border = element_rect(color = "grey40", fill=NA))

```
